Discovery of s-process stars in the LAMOST survey

### 2018-01-24 article/ms.tex
updates to methods

Barium giants form within a metallicity-dependent initial mass range (approximately 0.8 - 8$M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases. The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr. In contrast, metal rich, young observable stars may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.

@@

In this paper we analyse 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 967 s-process candidates including Barium stars, and exclusvely enhanced barium and strontium stars, respectively. Specifcally, the Barium star giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. Our exclusive barium and strontium candidates show s-process enhancement in 4554\AA \hspace{0.2mm} and 4934\AA for barium enhancement, and, 4554\AA \hspace{0.2mm} and 4215\AA for strontium enhancement. In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with Magellan. In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}

@@

\subsubsection{Candidate selection} \label{sec:cand}
The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. A negative residual as shown in the randomly selected Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm}, 4077\AA. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. We used five filters that each spectrum, for both enhancement lines, had to meet in order to be considered a s-process candidate; these included:

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must exceed A < -0.05.
\item Both amplittudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}($\lambda$ < 2).
\item Reduced $\chi^2$ from The Cannon must be < 3.
\item And, the LAMOST spectra must have a signal-to-noise ratio of S/N > 30 per pixel.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement, as listed in Table \ref{table:table1}.

>>>>

Barium giants form within a metallicity-dependent initial mass range (approximately $0.8 - 8\,M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases. The age of these stars vary considerably, with observable stars in metal-poor globular clusters hosting populations of $\approx$12Gyr. In contrast, metal rich, young observable stars may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.][]{whitelock2013}.

@@

In this paper we analyse 454,180 giant stars from the second LAMOST data release (DR) to identify and examine 967 s-process candidates including Barium stars, and exclusively enhanced barium and strontium stars, respectively. In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}

@@

\subsubsection{Candidate selection} \label{sec:cand}
The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA, respectively. A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, 4077\,\AA. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. Stars identified to just show high levels of barium required enhancement at both the 4554\,\AA\ and 4934\,\AA\ resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.

We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process candidate; these included:

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And finally, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement, as listed in Table \ref{table:table1}.
